---
title: "Case Study"
author: "Jeff Goldsmith"
date: "10/9/2018"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Load the data.

```{r}
library(p8105.datasets)
data(nyc_airbnb)
```


Data cleaning - Remove/clean some things
```{r}
nyc_airbnb <- nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group)

nyc_airbnb %>% 
  count(boro)

nyc_airbnb %>% 
  count(boro, neighbourhood) %>% 
  View
```

## Some questions
* Does rating differ by room type, neighborhood, or both?
* How does price relate to other variables?
* Where are the locations of rentals? Do locations differ by rental type?
* Where are the cheapest places? Most expensive?
* Most unfilled days?
* Which area has highest density?
* Host characteristics?

How many ppl have more than 1 listing?
```{r}
nyc_airbnb %>% 
  count(host_id, boro) %>% 
  filter(n > 1) %>% 
  count(boro)
```

Average rating by neighborhood?
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood, boro) %>% 
  summarize(avg_rate = mean(stars, na.rm = T)) %>% 
  arrange(desc(avg_rate)) %>% 
  ungroup() %>% 
  group_by(boro) %>% 
  summarize(boro_rate = mean(avg_rate, na.rm = T)) 
  
```

